This is an example of article title

### 2019-06-02 paper/paper.tex
tt

\section{SIMD sorting techniques}
\label{sec:methods}
%
\chipsort offers four high-level functions that can be used in applications as replacements for other sorting functions such as {\tt sort} in the Julia standard library. The {\tt chipsort!} function does not require any configuration and offers a great performance on a wide range of cases. The remaining functions are suitable for arrays of specific size ranges, and require choosing some numeric parameters. The function \verb chipsort_large  offers a good overview of all the techniques implemented in the module, and this section is structured according to its stages. Some of these techniques may also be useful in other applications instead of sorting, one clear example being the in-place matrix transpose.

@@

The function \verb chipsort_large  achieves sorting by first splitting the input array in chunks that are sorted separately with \verb chipsort_medium!  and then merged simultaneously. This inner sort is performed in multiple steps:
\begin{enumerate}
\item sorting small blocks of data with a sorting network;
\item reordering vectors in-place according to a matrix transpose;
\item vectorized Combsort with a limited number of iterations;
\item regular insertion sort until the whole data is sorted.
\end{enumerate}

@@

In \chipsort, as in the related work, parallelism is mainly exploited by carrying out the comparisons of the sorting network over vectors of size $V$ contained in SIMD registers, effectively running $V$ networks simultaneously. Other forms of instruction-level parallelism can also be in play, though. It may be possible to parallelize instructions such as \verb min  and \verb max , or the loading of data into registers. This is often done implicitly by the microarchitecture, and programmers can only make sure their code is suitable for this by properly ordering operations and avoiding branching, for instance. Part of this work is expected to be performed by the compiler, and in particular LLVM in the case of Julia.

\chipsort supports sorting networks of different sizes, currently only powers of 2, which are predefined as data structures in the file \href{https://github.com/nlw0/\chipsort.jl/blob/d2d049b7413f0073476021fa62fb748803130768/src/sorting-network-parameters.jl}{\tt sorting-network-parameters.jl}. The generated function \href{https://github.com/nlw0/\chipsort.jl/blob/d2d049b7413f0073476021fa62fb748803130768/src/sorting-networks.jl#L13}{\tt sort\_net} assigns each element of the sequence at each step to a variable, and the values from the next step are calculated according to the network specification. The comparisons are performed by the {\tt min} and {\tt max} functions, and the function is generic on the element types. Figure~\ref{fig:sort-net-listing} shows one example of generated code.

>>>>

\section{SIMD sorting techniques}
\label{sec:methods}
%
\chipsort offers four high-level functions that can be used in applications as replacements for other sorting functions such as {\tt sort} in the Julia standard library. The {\tt chipsort!} function does not require any configuration and offers a great performance on a wide range of cases. The remaining functions are suitable for arrays of specific size ranges, and require choosing some numeric parameters. The function {\tt chipsort\_large} offers a good overview of all the techniques implemented in the module, and this section is structured according to its stages. Some of these techniques may also be useful in other applications instead of sorting, one clear example being the in-place matrix transpose.

@@

The function {\tt chipsort\_large} achieves sorting by first splitting the input array in chunks that are sorted separately with {\tt chipsort\_medium!}  and then merged simultaneously. This inner sort is performed in multiple steps:
\begin{enumerate}
\item sorting small blocks of data with a sorting network;
\item reordering vectors in-place according to a matrix transpose;
\item vectorized Combsort with a limited number of iterations;
\item regular insertion sort until the whole data is sorted.
\end{enumerate}

@@

In \chipsort, as in the related work, parallelism is mainly exploited by carrying out the comparisons of the sorting network over vectors of size $V$ contained in SIMD registers, effectively running $V$ networks simultaneously. Other forms of instruction-level parallelism can also be in play, though. It may be possible to parallelize instructions such as {\tt min} and {\tt max}, or the loading of data into registers. This is often done implicitly by the microarchitecture, and programmers can only make sure their code is suitable for this by properly ordering operations and avoiding branching, for instance. Part of this work is expected to be performed by the compiler, and in particular LLVM in the case of Julia.

\chipsort supports sorting networks of different sizes, currently only powers of 2, which are predefined as data structures in the file \href{https://github.com/nlw0/chipsort.jl/blob/d2d049b7413f0073476021fa62fb748803130768/src/sorting-network-parameters.jl}{\tt sorting-network-parameters.jl}. The generated function \href{https://github.com/nlw0/chipsort.jl/blob/d2d049b7413f0073476021fa62fb748803130768/src/sorting-networks.jl#L13}{\tt sort\_net} assigns each element of the sequence at each step to a variable, and the values from the next step are calculated according to the network specification. The comparisons are performed by the {\tt min} and {\tt max} functions, and the function is generic on the element types. Figure~\ref{fig:sort-net-listing} shows one example of generated code.
